Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-02 Article/ici_submm_cloudcorr.tex
Final 1st draft

In this study, we present methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression(QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to current sensor MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is only partially successful in removing the cloud contamination. Though most of the cases with high cloud impact are corrected, cases with low cloud impact are only partially corrected. This is comparable/better to the level of accuracy achieved with operational cloud-filtering techniques, like scattering index. However with sub-mm channels, we are able to successfully correct most of the cases with cloud impact. The resulting error distributions are symmetric with very low spread. The methodology also works well even when only one of the higher frequencies is available. In some cases, the combination of 183\,GHz and sub-mm channels also results in a lower variability than noise.  Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for most of the scenes individually. Despite individual variations for each channel, it is observed that uncertainty consistently increases with the error in the performance. From data assimilation perspective, high quality cloud cleared radiances with symmetric error distribution and case-specific uncertainties are extremely valuable.

@@

Precipitation and most dense clouds, particularly if found at high altitude, can
still affect measured radiances around 183\,GHz
\citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
then is dominated by scattering, the complexity of the analysis of the data
increases dramatically and there exists a need to identify the problematic
cases. This is normally denoted as cloud filtering, to obtain data of ``clear
sky'' character. Such filtering has been applied to derive climate records
\citep{lang2020new} and is essential in studies of the agreement between
observations and simulations \citep{brogniez2016review} as well as 
comparing observations of different instruments to validate their calibration
\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. A commonly
used cloud filtering methods for these applications is the one of
\citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
involving rules on the brightness temperatures differences between channels. An
older version is \citet{burns1997effects}.

The main motivation for introducing 183\,GHz channels in operational sensors is
numerical weather prediction (NWP). Usage of passive microwave data by
``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
but 183\,GHz data are still mainly used in a clear sky fashion
\citep{geer2018all}. The later is particularly true in NWP of regional scope
\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
weather agencies will likely not be reached in many years. Anyhow, the cloud
filtering applied differs between NWP centres. One approach is to make use of a
``scattering index'' \citep{bennartz2002precipitation}, based on the
observations alone. Today, likely more common is to use ``observation minus
background'' (O-B), where the forecast model is used to obtain an estimate of
the expected clear-sky value and the observation is rejected if the deviation
exceeds some threshold (???). In both cases, the filtering typically involves
observations around 89 and/or 150\,GHz.

Despite the broad usage these filtering methods have some drawbacks. For
183\,GHz, the impact of hydrometeors systematically causes a decrease in the
observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This means that if any cloud
contamination is missed by the filtering this will cause a negative bias in
mean radiance, compared to the true clear-sky mean. This bias will translate to
a bias in humidity after the retrieval or assimilation. The alternative is to
apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected, i.e.\ an important loss of useful
data.

The filtering is normally done in a ``one for all'' manner, i.e.\ all 183\,GHz
channels are either kept or rejected, while, as the channels differ in their
altitude coverage, there could be cloud impact in some channels and still the
others can be considered as clear-sky. To allow a channel specific filtering,
data likely need to be combined in a more complex manner than simple
differences, but it is unclear what type of regression that would be best. This
points towards applying machine learning, as used by e.g.\
\citet{favrichon2019detecting}.

A maybe less obvious problem is the uncertainty to assign to the filtered
values. To our best knowledge, so far only estimates of mean and worst case
errors have been provided. Some cases with relatively high cloud impact will
likely be missed, while most cases are clear sky from start. As the remaining
cloudy cases can cause significant biases, the likely solution is to apply a
quite conservative (high) error estimate. However, this will unnecessary
downgrade the value of the truly clear sky cases and the observations are used
in a non-optimal manner.

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty.

This information can be used as a pure filter, by rejecting data where the
correction exceeds some threshold value. This threshold value should be
relatively low, to not introduce a bias in filtered dataset. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. This approach we denote as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

The estimation of NFCS values makes use of a special type of machine learning,
denoted as Quantile Regression Neural Network (QRNN,
\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
only some kind of best estimate is provided, QRNN works in a Bayesian fashion
and instead gives a description of the posterior uncertainty. More precisely,
QRNN outputs an user specified set of percentiles that gives a discrete
description posterior distribution, that can be process to derive e.g.\ the
expectation value.

The approach is demonstrated on a combination of 183\,GHz channels (following
\citet{buehler:aclou:07}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). \todo{Explain what sub-mm can
  do}.

The focus on ICI is motivated by several reasons. The true potential of the
QRNN cloud correction approach is likely not revealed if tested on existing
data and applying ICI data for cloud filtering has not earlier been discussed.
It is also argued that the cloud correction makes it possible to make good use
of ICI data already in clear-sky assimilation, a fact that should speed up the
use of this novel data source.

\section{Data and methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input. Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account, but the main difference is the concurrent utilisation of all 183\,GHz frequencies.      
\end{enumerate}

For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced.

@@

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution. A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we analyse both calibration plot and predicted errors to assess the correctness of predicted uncertainties.

@@

\section{Correcting cloud affected data in MWHS-2}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the methodology is expanded to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied to predict cloud free radiances. In this experiment, the training input includes all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction. This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is stronger as compared to 89\,GHz, and is less affected by surface emissivity. In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.

	\item The fourth experiment is based on the configuration QRNN-all. In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN. The use of 183\,GHz channels for ``self'' cloud filtering has been studied by  \citet{buehler:aclou:07}. They show that brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering. With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance. It should be noted that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately. Land/sea mask is also included in the training. This combination is denoted as 89+150+183\,GHz
\end{enumerate}

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of NFCS predictions to simulations. Results are for different QRNN experiments for MWHS-2 channel 14. The results from input channel combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz are with QRNN-single. While with QRNN-all, only combination 89+150+183\,GHz is shown. The statistics for uncorrected all-sky simulations and NFCS simulations are also provided. The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted. The fraction of rejected cases is given in parentheses. }
	\label{tab:error_statistics_mwhs_14}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
		\cline{2-11}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\
		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
		\middlehline
		bias     &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
		mae      &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
		std      &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
		\bottomhline
	\end{tabular}
\end{table*}

Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of QRNN predictions obtained from QRNN. The predicted values are able to remove most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The corresponding error statistics(Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, cloud impact causes a large negative skewness(-14.34) in the error distribution and the corresponding bias is -0.84\,K. Training QRNN with 89 and 150\,GHz removes a part of the cloud impact and reduces the bias to -0.09\,K, and the skewness is -1.11. The MAE and STD are also reduced. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric  error distributions, but the highest spread.

Further we investigated that if filtering the predictions with low accuracy could help in improving the error distribution. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold though the cases with high errors are removed, the negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

>>>>

Identification of cloud affected observations is indispensable for both clear-sky and all-sky Numerical Weather Prediction (NWP) systems. In this study, we present a methodology to identify and correct the cloud impact in microwave humidity radiances. A channel specific quantile regression neural network (QRNN) based approach is formulated to estimate the posterior distributions of noise free clear sky (NFCS) radiances. The applicability of the approach is demonstrated by application to a present sensor: MWHS-2. With the future outlook, the applicability to sub-millimeter (sub-mm) channels is also investigated. The results are compared against the NFCS simulations. With the present sensors, the approach is successful in correcting most of the cases with large negative departures, but a fraction cases end up with partial correction. In spite of the cases with residual cloud impact, the results from QRNN are better than what operational cloud filtering techniques like scattering index can achieve. On the other hand, when sub-mm observations from ICI are used to correct the cloud impact, QRNN can successfully correct most of the cases with cloud impact. Only 2-4\% of the cases are partially corrected and these can be easily removed by a simple filtering; and the resulting error distributions are almost symmetric with very low spread. The methodology also works well when only one of the higher frequencies (325\,GHz) is available. Except for the lowest peaking channel, using sub-mm observations results in error distributions with standard deviation less than the measurement noise. Another advantage of using QRNN is that predicted quantiles can be employed to quantify the case-specific uncertainty estimates. The results show that QRNN is successful in representing the uncertainty for each case individually. Despite individual variations for each channel, the predictions exhibit a higher uncertainty when the test data includes the ``out of distribution'' cases. In comparison to deterministic correction/filtering approaches, the high quality corrected radiances with uncertainty estimates have great potential to be used efficiently in assimilation systems.

@@

Although microwave channels are less affected by cloud contamination, precipitation and most dense clouds, particularly if found at high altitude, can
still affect measured radiances around 183\,GHz
\citep[e.g.][]{bennartz2003sensitivity}. As the impact from the hydrometeors
then is dominated by scattering, the complexity of the analysis of the data
increases dramatically and there exists a need to identify the problematic
cases. This is normally denoted as cloud filtering, to obtain data of ``clear
sky'' character. Such filtering has been applied to derive climate records
\citep{lang2020new} and is essential in studies of the agreement between
observations and simulations \citep{brogniez2016review} as well as 
comparing observations of different instruments to validate their calibration
\citep{john2013assessment,moradi:retri:15,berg2016intercalibration}. A commonly
used cloud filtering methods for these applications is the one of
\citet{buehler:aclou:07}. This method is based on the 183\,GHz data alone,
involving rules on the brightness temperatures differences between channels. An
older version is \citet{burns1997effects}.

Another motivation necessitating the need for cloud clearing is usage of 183\,GHz channels in 
numerical weather prediction (NWP). Usage of passive microwave data by
``all-sky'' assimilation in global NWP is growing in \citep{geer2017growing},
but 183\,GHz data are still mainly used in a clear sky fashion
\citep{geer2018all}. The latter is particularly true in NWP of regional scope
\citep{gustafsson2018survey}, all-sky assimilation of 183\,GHz at many national
weather agencies will likely not be reached in many years. Anyhow, both clear-sky and all-sky assimilation require identification of cloud affected observations. ``Scattering index'' \cite{geer2015scatteringindex} is one of the approaches used. It is based on brightness temperature differences between 89 and 150\,GHz. Another commonly used cloud filtering method is based on ``observation minus background'' (O-B), where the forecast model is used to obtain an estimate of the expected clear-sky value and the observation is rejected if the deviation exceeds some threshold \citep{English1999clouddetection}.

Despite their broad usage, these filtering methods aim at partial removal of cloud contamination. The residual cloud impact can have some drawbacks. For 183\,GHz, the impact of hydrometeors systematically causes a decrease in the observed radiance (maybe with exceptions at extremely dry conditions), see
e.g.\ \citet{barlakas:three:20} and below. This implies that if any cloud contamination is missed by the filtering this will cause a negative bias in mean radiance, compared to the true clear-sky mean. This bias will translate to a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds is overcome by inflating the observational errors. However this artificial suppression of observations diminishes the impact of observations.  The alternative is to apply a very strict filtering, but this will result in that a high fraction of
actually clear-sky values will be rejected, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression that would be best. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the uncertainty to assign to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors have been provided. Some cases with relatively high cloud impact will likely be missed, while most cases are clear sky from start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessary downgrade the value of the truly clear sky cases and the observations are used in a non-optimal manner.

We are here approaching cloud filtering task from a new angle. The basic idea
is to derive an estimate of the corresponding noise-free clear-sky (NFCS) value
(i.e.\ the radiance that would have been measured in absence of noise and
hydrometeors). This is done for each channel separately, only using
measurements (no ``background'' data involved). Not only a best estimate is
provided, but also a case specific uncertainty. This information can be used as a pure filter, by rejecting data where the correction exceeds some threshold value. This threshold value should be
relatively low, to not introduce a bias in filtered dataset. However, even
better is to replace the original value with the predicted NFCS value when
forming the clear-sky dataset. We denote this approach as cloud correction. It
is shown below that a basically bias free cloud correction can be obtained.
This feature removes the need of threshold value, as long as the retrieval or
assimilation system can incorporate the uncertainty of the corrected value. As
also will be shown, the uncertainty for originally clear sky data is determined
by noise, but the uncertainty increases with magnitude of correction.
Accordingly, the cloud correction approach allows that the full weight of
clear-sky data can be preserved.

The estimation of NFCS values makes use of a special type of machine learning,
denoted as Quantile Regression Neural Network (QRNN,
\citet{pfreundschuh:aneur:18}). Unlike standard usage of machine learning where
only some kind of best estimate is provided, QRNN works in a Bayesian fashion
and instead gives a description of the posterior uncertainty. More precisely,
QRNN outputs an user specified set of quantiles that gives a discrete
description posterior distribution, that can be processed to derive e.g.\ the
expectation value.

The approach is demonstrated with use of 89 and 150\,GHz channels (following
\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as AWS, presented below). The focus on sub-mm channels is motivated by several reasons.  Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors. For high altitude cirrus clouds, the these frequencies have a stronger signal than 183\,Ghz. In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher. Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing
data and applying ICI data for cloud filtering has not earlier been discussed. It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.

A description of data and QRNN is provided in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the applicabity of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.
\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder 2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
MicroWave Humidity Sounder 2 (MWHS-2) is an instrument onboard FengYun-3C (FY-3C). MWHS-2 is designed to observe the distribution of global atmospheric thermodynamics information, and monitor the severe convective systems. It is a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz and eight temperature sounding channels are centered at 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to MWS (Micro Wave Sounder) and ATMS (Advanced Technology Microwave Sounder). As of December 2019, observations from MWHS-2 are routinely assimilated at ECMWF \citep{duncan2020MWHS}. The channels relevant to this study are described on Table~\ref{tab:specifications_MWHS2}.

@@

	\item QRNN-all: In this configuration, all-sky brightness temperatures from all available 183\,GHz channels are included in the training input. Just like QRNN-single, data from other non-humidity channels and additional data are also taken into account; but the main difference is the concurrent utilisation of all 183\,GHz frequencies.      
\end{enumerate}

For all three sensors described in this study, one or both of the above QRNN configurations are used. The selection of input channels is sensor dependent and is described in detail when introduced later.

@@

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution. A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.

@@

\section{Correcting cloud affected data in MWHS-2}
\label{qrnn_mwhs}
%
In this section, we introduce the QRNN based cloud  correction in the context of current operational sensors.  We use MWHS-2 to demonstrate the results. The choice is motivated by the fact that MWHS-2 has five complementary 183\,GHz channels as ATMS/MWS, along with additional 118\,GHz channel. In order to formulate and test the correction approach, multiple QRNN experiments are performed for MWHS-2 channel 14. Later the methodology is extended to other 183\,GHz channels. A brief comparison of the results is also made against existing cloud filtering methods. Further, the estimates of case-specific uncertainties obtained from QRNN are also evaluated.

@@

	\item In the first experiment, we examine the performance of QRNN cloud correction with MWHS-2 window channels: 89 and 150\,GHz. In ECMWF NWP system, the differences between the observations of these two window channels (Scattering Index) \citep{Lu2015FY3C} are used to identify the cloud affected data for ATMS, MHS and MWHS-2. To investigate the potential impact of these two window channels in QRNN based cloud correction, the configuration QRNN-single is applied. In this experiment, the training inputs include all-sky brightness temperatures from target 183\,GHz channel, 89\,GHz and 150\,GHz. Both 89 and 150\,GHz are window channels so the land sea mask is also included as a training input. For example, for channel 14, the training inputs are all-sky brightness temperatures from channels 14, 1, 10 and land/sea mask. This combination is referred as 89+150\,GHz in the text.

@@

	\item The third experiment is designed to assess the exclusive impact of 150\,GHz in cloud correction. This experiment is motivated by the fact that hydrometeor impact at 150\,GHz is strongest as compared to 89\,GHz and other 118\,GHz channels; and is less affected by surface emissivity. In this experiment, QRNN-single is trained with brightness temperatures from 150\,GHz along with the target channel and land/sea mask.

	\item The fourth experiment is based on the configuration QRNN-all. In this experiment, we use 89 and 150\,GHz channels along with all 183\,GHz channels to train QRNN. The use of 183\,GHz channels for ``self'' cloud filtering has been studied by  \citet{buehler:aclou:07}. They show that brightness temperatures between outer and inner humidity channels can be used as a criterion for cloud filtering. With QRNN-all, we investigate if additional humidity channels in the training process can improve the performance. Note that though the training inputs are same for each 183\,GHz channel, the output is the target 183\,GHz channel; thus each channel still needs to be trained separately. Land/sea mask is also included in the training. This combination is denoted as 89+150+183\,GHz
\end{enumerate}

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[height=55mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{Distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{Error statistics for deviations of NFCS predictions to simulations. Results are for different QRNN experiments for MWHS-2 channel 14. The results from input channel combinations 89+150\,GHz, 89+150+118\,GHz and 150\,GHz are with QRNN-single. While with QRNN-all, only combination 89+150+183\,GHz is shown. The statistics for uncorrected all-sky simulations and NFCS simulations are also provided. The label ``All'' refers to entire predicted dataset, while Filtered(5\,K) denotes the subset where predictions with correction greater than 5\,K are omitted. The fraction of rejected cases is given in parentheses. }
	\label{tab:error_statistics_mwhs_14}
	\begin{tabular}{lrr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c}{QRNN-all}\\
		\cline{2-11}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c}{89+150+183\,GHz}\\
		&			   &			& All & Filtered(5K) & All & Filtered(5K) & All & Filtered(5K)  & All & Filtered(5K)\\
		\middlehline
		Bias      &  0.00 &  -0.84 & -0.09 & -0.08(3.3\%) & -0.04 & -0.03(3.4\%) & -0.09 & -0.09(3.2\%) & -0.09(3.3\%) & -0.08(3.3\%)  \\
		MAE       &  0.80 &   1.45 &  0.88 &  0.86 &  0.89 &  0.87 &  0.89 &  0.87 &  0.62 &  0.59\\
		STD       &  1.00 &   3.90 &  1.19 &  1.14 &  1.19 &  1.15 &  1.21 &  1.16 &  0.90 &  0.83\\
		skewness & -0.00 & -14.34 & -1.11 & -0.93 & -1.00 & -0.84 & -0.88 & -0.98 & -1.58 & -1.62\\
		\bottomhline
	\end{tabular}
\end{table*}

Fig.~\ref{fig:distribution_predicted_mwhs14} shows the distribution of point estimates obtained from QRNN. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The corresponding error statistics(see Sect.~\ref{sec:validation}) are displayed in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric  error distributions, but the highest spread.

Further we investigated that if filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are cases associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI)  \citep{geer2015scatteringindex} and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ and $183.31\pm 1.00$ as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in Table~\ref{tab:SI_statistics}. 
With SI threshold = 5\,K, almost 30\% of the data is rejected, yet the resulting error distributions are worse as compared to QRNN. Similar is the case with B183, where approximately 17\% of the data is rejected, but the filtering performance is inadequate.
